### 2014-05-02 acknowledgements.tex
moved John Madded to author list and added Evan as an author

\section*{Acknowledgements} 
The authors would like to thank Siemens Medical Solution USA, Ultrasound
Division for their in-kind technical support.  Special thanks to Ned Danieley
for computer system administration support, the pathology assistants and Dr.
John Madden in the Duke University Medical Center for their gross prostate
organ processing, and Matthew Brown for his assistance in designing the optical
prostate rotation feedback system.  This work was supported by NIH R01CA142824
and the Duke Coulter Translational Grant Program.

>>>>

\section*{Acknowledgements} 
The authors would like to thank Siemens Medical Solution USA, Ultrasound
Division for their in-kind technical support.  Special thanks to Ned Danieley
for computer system administration support, the pathology assistants in the
Duke University Medical Center for their gross prostate organ processing, and
Matthew Brown for his assistance in designing the optical prostate rotation
feedback system.  This work was supported by NIH R01CA142824 and the Duke
Coulter Translational Grant Program.
